\textsc{Beyond the Iceberg Hypothesis: \\Opening the Black Box of Transport Costs}

### 2017-07-27 redaction/dhp_july2017.tex
modifsJH270717
dernières modifs paper.

@@

%\todo{Changer la facon de presenter les resultats, pour harmoniser avec la facon de faire dans le corps du papier. Jerome?}
\begin{table}[htbp]
  \centering
  \caption{Air: Transport costs estimates, 3-digits (selected years)}
\begin{center}
    \begin{tabular}{l|cccccc}
\hline\hline

Year & 1974  & 1980  & 1990  & 2000  & 2010  & 2013   \\ 
\hline
\multicolumn{7}{l}{\textbf{Model (A) - With only Ad-Valorem Transport Costs} ($\widehat{\tau}^{ice}$, in \%)}     \\ 
\hline
Mean  & 6.9& 5.4 &5.0 & 3.6 & 4.2 & 3.4  \\
Median & 5.4 & 3.8 & 4.4 & 2.5 & 3.4 & 2.9  \\
%Standard Error & 0.052 & 0.049 & 0.039 & 0.033 & 0.037 & 0.024 \\
\hline
\multicolumn{7}{l}{\textbf{Model (B) - With Additive \& Ad-Valorem Transport Costs}}    \\ 
\hline
\multicolumn{7}{l}{\textit{Ad-valorem term ($\widehat{\tau}^{adv}$, in \%)}}  \\ \hline
Mean & 3.6 & 2.3 & 2.4 &1.7 & 2.6 & 1.7  \\
Median & 2.7 & 1.6 & 1.6 & 1.2 & 2.2 & 1.7 \\
%Standard Error & 0.032 & 0.025 & 0.021 & 0.016 & 0.023 & 0.012  \\

\hline
\multicolumn{7}{l}{\textit{Additive term ($\widehat{t}^{add}/\widetilde{p}$, in \%)}}     \\ \hline
Mean & 2.6 & 2.0 & 1.8 & 1.3 & 1.1 & 1.0  \\
Median & 1.1 & 0.5 & 0.8 & 0.5 & 0.4 & 0.5  \\
%\multicolumn{1}{l}{Standard Error} & 0.040 & 0.041 & 0.033 & 0.028 & 0.024 & 0.020  \\ 
\hline
\# observations & 14955 & 16118 & 24958 & 35027 & 40279 & 39351  \\
\hline\hline
\multicolumn{7}{l}{\parbox[l]{11cm}{ \vspace{7pt}\scriptsize{Notes: Statistics are obtained weighting each observation by its value in transport (mode-dependent). Additive term expressed in fraction of fas price.}}}
\end{tabular}%
\end{center}
\label{tab:result_air_3d_detail}
\end{table}%

%%%JH 26/07 : Reprendre XXX ICI XXX

\begin{table}[htbp]
  \centering
  \caption{Vessel: Transport costs estimates, 3 digit (selected years)}
\begin{center}
    \begin{tabular}{l|cccccc}
   \hline\hline
Year         & 1974  & 1980  & 1990  & 2000  & 2010  & 2013   \\
 \hline
   \multicolumn{7}{l}{\textbf{With only Iceberg Trade Costs} }  \\
Mean  & 1.098 & 1.065 & 1.057 & 1.051 & 1.040 & 1.036  \\
Median & 1.096 & 1.055 & 1.046 & 1.049 & 1.036 & 1.033  \\
Standard Error & 0.053 & 0.040 & 0.032 & 0.028 & 0.020 & 0.018  \\
\multicolumn{7}{l}{\textbf{With Additive \& Iceberg Trade Costs} }    \\
\hline
\multicolumn{7}{l}{\textit{Additive term } }  \\ \hline
Mean  & 0.051 & 0.034 & 0.027 & 0.028 & 0.025 & 0.015  \\
Median & 0.029 & 0.023 & 0.017 & 0.022 & 0.019 & 0.008 \\
Standard Error & 0.085 & 0.046 & 0.040 & 0.043 & 0.025 & 0.020 \\ \hline
\multicolumn{7}{l}{\textit{Iceberg term} } \\ \hline
Mean  & 1.054 & 1.031 & 1.033 & 1.025 & 1.019 & 1.022 \\
Median & 1.049 & 1.024 & 1.028 & 1.021 & 1.018 & 1.018  \\
Standard Error & 0.041 & 0.023 & 0.022 & 0.021 & 0.018 & 0.018  \\
\hline
 \# obs & 19007 & 17356 & 28383 & 36090 & 37748 & 38473 \\ \hline
\hline\hline
\multicolumn{7}{l}{\parbox[l]{11cm}{ \vspace{7pt}\scriptsize{Notes: Statistics are obtained weighting each observation by its value in transport (mode-dependent). Additive term expressed in fraction of fas price.}}}
\end{tabular}%
\end{center} \label{tab:result_ves_3d_detail}
\end{table}%

@@

Two interesting results emerge from Figure \ref{fig:decomp_variance}. First, the share of the cif-fas price gap variance that comes from the variance between products (5-digit level) is of same magnitude of order at the variance between sectors at the 3-digit level. Both account for between 30 and 40\% of the total variance in Air transport, depending on the years considered. This is also the case for Ocean transport, even if the difference between the between-country variance share and the between-sector share is more pronounced (30\% for the between-sector vs 40\% for the between-product variance at the beginning of the period). This delivers an indirect robustness check to the degree of classification we have retained to estimate international transport costs. Second, the variance of the cif-fas price gap that can be attributed to the product (or sector) dimension is much larger that the between-country variance. This holds throughout the period and for both transport modes. This suggests that what primarily matters in international transport costs is mostly attributable to the product per se, rather than to the country where it comes from. By extension, one can expect a limited role of distance and other country-related variables as determinants of transport costs.

@@

\begin{table}[htbp]
  \centering
  \caption{Air: Transport costs estimates, Selected years, 4-digit}
\begin{center}
    \begin{tabular}{l|cccccc}
   \hline\hline
Year & 1974  & 1981  & 1989  & 2001  & 2009  & 2013 \\ \hline
\multicolumn{7}{l}{\textbf{With only Iceberg Trade Costs} }  \\
Mean  & 1.066 & 1.058 & 1.052 & \multicolumn{1}{c}{1.033} & \multicolumn{1}{c}{1.037} & \multicolumn{1}{c}{1.032} \\
Median & 1.052 & 1.044 & 1.041 & \multicolumn{1}{c}{1.021} & \multicolumn{1}{c}{1.027} & \multicolumn{1}{c}{1.026}  \\
Standard Error & 0.056 & 0.054 & 0.046 & \multicolumn{1}{c}{0.040} & \multicolumn{1}{c}{0.036} & \multicolumn{1}{c}{0.025}  \\
\hline
\multicolumn{7}{l}{\textbf{With Additive \& Iceberg Trade Costs }}  \\ \hline
\multicolumn{7}{l}{\textit{Iceberg term} }   \\ \hline
Mean  & 1.035 & 1.026 & 1.031 & \multicolumn{1}{c}{1.015} & \multicolumn{1}{c}{1.021} & \multicolumn{1}{c}{1.016}  \\
Median & 1.025 & 1.017 & 1.019 & \multicolumn{1}{c}{1.010} & \multicolumn{1}{c}{1.017} & \multicolumn{1}{c}{1.014}  \\
Standard Error & 0.036 & 0.028 & 0.030 & \multicolumn{1}{c}{0.021} & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.015}  \\ \hline
\multicolumn{7}{l}{\textit{Additive term} }   \\ \hline
Mean  & 0.026 & 0.021 & 0.017 & \multicolumn{1}{c}{0.012} & \multicolumn{1}{c}{0.012} & \multicolumn{1}{c}{0.010} \\
Median & 0.012 & 0.006 & 0.006 & \multicolumn{1}{c}{0.005} & \multicolumn{1}{c}{0.004} & \multicolumn{1}{c}{0.004}  \\
Standard Error & 0.039 & 0.042 & 0.033 & \multicolumn{1}{c}{0.027} & \multicolumn{1}{c}{0.029} & \multicolumn{1}{c}{0.019} \\ \hline
\# obs & 14944 & 16844 & 25307 & \multicolumn{1}{c}{35005} & \multicolumn{1}{c}{38475} & \multicolumn{1}{c}{39460}  \\
\hline\hline
\multicolumn{7}{l}{\parbox[l]{11cm}{ \vspace{7pt}\scriptsize{Notes: Statistics are obtained weighting each observation by its value in transport (mode-dependent). Additive term expressed in fraction of fas price.}}}
\end{tabular}%
\end{center}
  \label{tab:result_air_rob}
\end{table}%

\begin{table}[htbp]
  \centering
\caption{Vessel: Transport costs estimates, Selected years, 4-digit}
\begin{center}
    \begin{tabular}{l|cccccc}
   \hline\hline
Year & 1974  & 1981  & 1989  & 2001  & 2009  & 2013 \\
\hline
\multicolumn{7}{l}{\textbf{With only Iceberg Trade Costs}} \\
Mean  & 1.098 & 1.061 & \multicolumn{1}{c}{1.058} & \multicolumn{1}{c}{1.051} & \multicolumn{1}{c}{1.042} & \multicolumn{1}{c}{1.036}  \\
Median & 1.094 & 1.051 & \multicolumn{1}{c}{1.048} & \multicolumn{1}{c}{1.045} & \multicolumn{1}{c}{1.038} & \multicolumn{1}{c}{1.031} \\
Standard Error & 0.060 & 0.038 & \multicolumn{1}{c}{0.036} & \multicolumn{1}{c}{0.030} & \multicolumn{1}{c}{0.023} & \multicolumn{1}{c}{0.020} \\
\hline
\multicolumn{7}{l}{\textbf{With Additive \& Iceberg Trade Costs } }\\ \hline
\textit{Iceberg term} &       &       &       &       &       &     \\
Mean  & 1.054 & 1.034 & \multicolumn{1}{c}{1.028} & \multicolumn{1}{c}{1.028} & \multicolumn{1}{c}{1.024} & \multicolumn{1}{c}{1.021}  \\
Median & 1.049 & 1.030 & \multicolumn{1}{c}{1.024} & \multicolumn{1}{c}{1.025} & \multicolumn{1}{c}{1.026} & \multicolumn{1}{c}{1.018} \\
Standard Error & 0.043 & 0.026 & \multicolumn{1}{c}{0.025} & \multicolumn{1}{c}{0.021} & \multicolumn{1}{c}{0.016} & \multicolumn{1}{c}{0.013}  \\
\textit{Additive term} &       &       &       &       &       &     \\
Mean  & 0.046 & 0.026 & \multicolumn{1}{c}{0.031} & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.021} & \multicolumn{1}{c}{0.015}  \\
Median & 0.029 & 0.013 & \multicolumn{1}{c}{0.019} & \multicolumn{1}{c}{0.015} & \multicolumn{1}{c}{0.013} & \multicolumn{1}{c}{0.008} \\
Standard Error & 0.068 & 0.044 & \multicolumn{1}{c}{0.037} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.031} & \multicolumn{1}{c}{0.023} \\ \hline
\# obs & 19196 & 17916 & \multicolumn{1}{c}{29387} & \multicolumn{1}{c}{36677} & \multicolumn{1}{c}{37643} & \multicolumn{1}{c}{38820} \\
\hline\hline
\multicolumn{7}{l}{\parbox[l]{11cm}{ \vspace{7pt}\scriptsize{Notes: Statistics are obtained weighting each observation by its value in transport (mode-dependent). Additive term expressed in fraction of fas price.}}}
\end{tabular}%
\end{center}
\label{tab:result_ves_rob}%
\end{table}%

@@

We now report the goodness-of-fit exercise (conducted by transport mode) at the 4-digit product classification level (for the selected years). The results are reported in Tables \ref{tab:good_fit_air_rob} (for Air) and \ref{tab:good_fit_ves_rob} (for Vessel).
\begin{table}[htbp]
  \centering
  \caption{Air: Measures of Goodness-of-fit, 4-digits}
\begin{center}
\label{tab:good_fit_air_rob}%
%\vspace{0.5cm}
%\scalebox{0.97}{
\begin{tabular}{l|cccccc}
\hline
\hline
      & \multicolumn{6}{c}{Year}              \\
      & \multicolumn{1}{c}{1974} & \multicolumn{1}{c}{1981} & \multicolumn{1}{c}{1989} & \multicolumn{1}{c}{2001} & \multicolumn{1}{c}{2009} & \multicolumn{1}{c}{2013}  \\
\hline
\textbf{R2} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &       &       &      \\
Term I only & \multicolumn{1}{c}{0.48} & \multicolumn{1}{c}{0.49} & \multicolumn{1}{c}{0.50} & \multicolumn{1}{c}{0.50} & \multicolumn{1}{c}{0.45} & \multicolumn{1}{c}{0.35} \\
Terms A \& I & \multicolumn{1}{c}{0.63} & \multicolumn{1}{c}{0.66} & \multicolumn{1}{c}{0.65} & \multicolumn{1}{c}{0.66} & \multicolumn{1}{c}{0.54} & \multicolumn{1}{c}{0.45} \\
\textbf{SER} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &       & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}  \\
Term I only & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &       & \multicolumn{1}{c}{0.88} & \multicolumn{1}{c}{0.93}  \\
Terms A \& I & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &       & \multicolumn{1}{c}{0.80} & \multicolumn{1}{c}{0.86}  \\
\textbf{Log-likelihood} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &       & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
Term I only & \multicolumn{1}{c}{-17505.55} & \multicolumn{1}{c}{-21813.46} & \multicolumn{1}{c}{-30960.56} & \multicolumn{1}{c}{-44067.62} & \multicolumn{1}{c}{-49375.57} & \multicolumn{1}{c}{-53197.87}  \\
Terms A\& I & \multicolumn{1}{c}{-14895.81} & \multicolumn{1}{c}{-18589.91} & \multicolumn{1}{c}{-26553.53} & \multicolumn{1}{c}{-37297.93} & \multicolumn{1}{c}{-45747.57} & \multicolumn{1}{c}{-49899.14}  \\
\textbf{AIC criteria} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &       & \multicolumn{1}{c}{}  \\
Term I only & \multicolumn{1}{c}{36243.10} & \multicolumn{1}{c}{44966.91} & \multicolumn{1}{c}{63417.12} & \multicolumn{1}{c}{89747.24} & \multicolumn{1}{c}{100317.13} & \multicolumn{1}{c}{107963.73} \\
Terms A \& I & \multicolumn{1}{c}{31873.63} & \multicolumn{1}{c}{39495.82} & \multicolumn{1}{c}{55777.05} & \multicolumn{1}{c}{77439.85} & \multicolumn{1}{c}{94059.14} & \multicolumn{1}{c}{102224.28}  \\
\textbf{Test LL} &       &       &       &       &       &       \\
2$\times$(ll(UR) -ll(R)) & \multicolumn{1}{c}{5219.47} & \multicolumn{1}{c}{6447.09} & \multicolumn{1}{c}{8814.06} & \multicolumn{1}{c}{13539.39} & \multicolumn{1}{c}{7255.99} & \multicolumn{1}{c}{6597.45}  \\
\# restrictions  & \multicolumn{1}{c}{640} & \multicolumn{1}{c}{698} & \multicolumn{1}{c}{778} & \multicolumn{1}{c}{833} & \multicolumn{1}{c}{824} & \multicolumn{1}{c}{818}  \\
p-value & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.000} \\
\hline\hline
\multicolumn{7}{l}{\parbox[l]{15cm}{ \vspace{7pt}\scriptsize{Notes: R$^{2}$ between the log of predicted ratio and the log of the observed ratio. The number \# of restrictions is equal to the number of parameters estimated, i.e., the number of partner countries plus the number of products.}}}
\end{tabular}%
\end{center}
\end{table}%

>>>>

\newcommand\cites[1]{\citeauthor{#1}'s\ (\citeyear{#1})}

\newcommand\citeh[1]{\citeauthor{#1}'\ (\citeyear{#1})}

@@

%\todo{Changer la facon de presenter les resultats, pour harmoniser avec la facon de faire dans le corps du papier. Jerome?}
\begin{table}[htbp]
  \centering
  \caption{Air: Transport costs estimates, 3-digits (selected years)}
\begin{center}
    \begin{tabular}{l|cccccc}
\hline\hline
Year & 1974  & 1980  & 1990  & 2000  & 2010  & 2013   \\
\hline
\multicolumn{7}{l}{\textbf{Model (A) - With only Ad-Valorem TC} ($\widehat{\tau}^{ice}$, in \%)}     \\
\hline
Mean  & 6.9& 5.4 &5.0 & 3.6 & 4.2 & 3.4  \\
Median & 5.4 & 3.8 & 4.4 & 2.5 & 3.4 & 2.9  \\
%Standard Error & 0.052 & 0.049 & 0.039 & 0.033 & 0.037 & 0.024 \\
\hline
\multicolumn{7}{l}{\textbf{Model (B) - With Additive \& Ad-Valorem TC}}    \\
\hline
\multicolumn{7}{l}{\textit{Ad-valorem term ($\widehat{\tau}^{adv}$, in \%)}}  \\ \hline
Mean & 3.6 & 2.3 & 2.4 &1.7 & 2.6 & 1.7  \\
Median & 2.7 & 1.6 & 1.6 & 1.2 & 2.2 & 1.7 \\
%Standard Error & 0.032 & 0.025 & 0.021 & 0.016 & 0.023 & 0.012  \\

\hline
\multicolumn{7}{l}{\textit{Additive term ($\widehat{t}^{add}/\widetilde{p}$, in \%)}}     \\ \hline
Mean & 2.6 & 2.0 & 1.8 & 1.3 & 1.1 & 1.0  \\
Median & 1.1 & 0.5 & 0.8 & 0.5 & 0.4 & 0.5  \\
%\multicolumn{1}{l}{Standard Error} & 0.040 & 0.041 & 0.033 & 0.028 & 0.024 & 0.020  \\
\hline
\# observations & 14955 & 16118 & 24958 & 35027 & 40279 & 39351  \\
\hline\hline
\multicolumn{7}{l}{\parbox[l]{11cm}{ \vspace{7pt}\scriptsize{Notes: TC = Transport Costs. Statistics are obtained weighting each observation by its value in transport (mode-dependent). Additive term expressed in fraction of fas price.}}}
\end{tabular}%
\end{center}
\label{tab:result_air_3d_detail}
\end{table}%

\begin{table}[htbp]
  \centering
  \caption{Vessel: Transport costs estimates, 3 digit (selected years)}
\begin{center}
    \begin{tabular}{l|cccccc}
   \hline\hline
Year         & 1974  & 1980  & 1990  & 2000  & 2010  & 2013   \\
 \hline
   \multicolumn{7}{l}{\textbf{Model (A) - With only Ad-Valorem TC} ($\widehat{\tau}^{ice}$, in \%)}  \\
   \hline
Mean  & 9.8 & 6.5 & 5.7 & 5.1 & 4.0 & 3.6  \\
Median & 9.6 & 5.5 & 4.6 & 4.9 & 3.6 & 3.3  \\
%Standard Error & 5.3 & 4.0 & 3.2 & 2.8 & 2.0 & 1.8  \\
\hline
\multicolumn{7}{l}{\textbf{Model (B) - With Additive \& Ad-Valorem TC}}    \\
\hline
\multicolumn{7}{l}{\textit{Ad-valorem term ($\widehat{\tau}^{adv}$, in \%)} } \\
\hline
Mean  & 5.4 & 3.1 & 3.3 & 2.5 & 1.9 & 2.2 \\
Median & 4.9 & 2.4 & 2.8 & 2.1 & 1.8 & 1.8  \\
%Standard Error & 0.041 & 0.023 & 0.022 & 0.021 & 0.018 & 0.018  \\
\hline
\multicolumn{7}{l}{\textit{Additive term ($\widehat{t}^{add}/\widetilde{p}$, in \%)}}  \\
\hline
Mean  & 5.1 & 3.4 & 2.7 & 2.8 & 2.5 & 1.5  \\
Median & 2.9 & 2.3 & 1.7 & 2.2 & 1.9 & 0.8 \\
%Standard Error & 0.085 & 0.046 & 0.040 & 0.043 & 0.025 & 0.020 \\
\hline
 \# observations & 19007 & 17356 & 28383 & 36090 & 37748 & 38473 \\
\hline\hline
\multicolumn{7}{l}{\parbox[l]{11cm}{ \vspace{7pt}\scriptsize{Notes: TC = Transport Costs. Statistics are obtained weighting each observation by its value in transport (mode-dependent). Additive term expressed in fraction of fas price.}}}
\end{tabular}%
\end{center} \label{tab:result_ves_3d_detail}
\end{table}%

@@

Two interesting results emerge from Figure \ref{fig:decomp_variance}. First, the share of the cif-fas price gap variance that comes from the variance between products (5-digit level) is of same magnitude of order at the variance between sectors at the 3-digit level. Both account for between 30 and 40\% of the total variance in Air transport, depending on the years considered. This is also the case for vessel transport, even if the difference between the between-product variance share and the between-sector share is more pronounced (30\% for the between-sector vs 40\% for the between-product variance at the beginning of the period). This delivers an indirect robustness check to the degree of classification we have retained to estimate international transport costs. Second, the variance of the cif-fas price gap that can be attributed to the product (or sector) dimension is much larger that the between-country variance. This holds throughout the period and for both transport modes. This suggests that what primarily matters in international transport costs is mostly attributable to the product per se, rather than to the country where it comes from. By extension, one can expect a limited role of distance and other country-related variables as determinants of transport costs.

@@

\begin{table}[htbp]
  \centering
  \caption{Air: Transport costs estimates, Selected years, 4-digit}
\begin{center}
    \begin{tabular}{l|cccccc}
   \hline\hline
Year & 1974  & 1981  & 1989  & 2001  & 2009  & 2013 \\ \hline
\multicolumn{7}{l}{\textbf{Model (A) - With only Ad-Valorem TC} ($\widehat{\tau}^{ice}$, in \%) }  \\
\hline
Mean  & 6.6 & 5.8 & 5.2 & 3.3 & 3.7 & 3.2 \\
Median & 1.052 & 1.044 & 1.041 & 2.1 & 2.7 & 2.6 \\
%Standard Error & 0.056 & 0.054 & 0.046 & \multicolumn{1}{c}{0.040} & \multicolumn{1}{c}{0.036} & \multicolumn{1}{c}{0.025}  \\
\hline
\multicolumn{7}{l}{\textbf{Model (B) - With Additive \& Ad-Valorem TC}}  \\ \hline
\multicolumn{7}{l}{\textit{Ad-valorem term ($\widehat{\tau}^{adv}$, in \%} }   \\ \hline
Mean  & 3.5 & 2.6 & 3.1 & 1.5 & 2.1 & 1.6  \\
Median & 2.5 & 1.7 & 1.9 & 1.0 & 1.7 & 1.4  \\
%Standard Error & 0.036 & 0.028 & 0.030 & \multicolumn{1}{c}{0.021} & \multicolumn{1}{c}{0.024} & \multicolumn{1}{c}{0.015}  \\ 
\hline
\multicolumn{7}{l}{\textit{Additive term ($\widehat{t}^{add}/\widetilde{p}$, in \%} }   \\ \hline
Mean  & 2.6 & 2.1 & 1.7 & 1.2 &1.2 & 1.0 \\
Median & 1.2 & 0.6 & 0.6 & 0.5 & 0.4 & 0.4  \\
%Standard Error & 0.039 & 0.042 & 0.033 & \multicolumn{1}{c}{0.027} & \multicolumn{1}{c}{0.029} & \multicolumn{1}{c}{0.019} \\ 
\hline
\# observations & 14944 & 16844 & 25307 & \multicolumn{1}{c}{35005} & \multicolumn{1}{c}{38475} & \multicolumn{1}{c}{39460}  \\
\hline\hline
\multicolumn{7}{l}{\parbox[l]{11cm}{ \vspace{7pt}\scriptsize{Notes: TC = Transport Costs. Statistics are obtained weighting each observation by its value in transport (mode-dependent). Additive term expressed in fraction of fas price.}}}
\end{tabular}%
\end{center}
  \label{tab:result_air_rob}
\end{table}%

\begin{table}[htbp]
  \centering
\caption{Vessel: Transport costs estimates, Selected years, 4-digit}
\begin{center}
    \begin{tabular}{l|cccccc}
   \hline\hline
Year & 1974  & 1981  & 1989  & 2001  & 2009  & 2013 \\
\hline
\multicolumn{7}{l}{\textbf{Model (A) - With only Ad-Valorem TC} ($\widehat{\tau}^{ice}$, in \%)} \\
Mean  & 9.8 & 6.1 & 5. & 5.1 & 4.2 & 3.6  \\
Median & 9.4 & 5.1 & 4.8 & 4.5 & 3.8 & 3.1 \\
%Standard Error & 0.060 & 0.038 & \multicolumn{1}{c}{0.036} & \multicolumn{1}{c}{0.030} & \multicolumn{1}{c}{0.023} & \multicolumn{1}{c}{0.020} \\
\hline
\multicolumn{7}{l}{\textbf{Model (B) - With Additive \& Ad-Valorem TC} }\\ \hline
\multicolumn{7}{l}{\textit{Ad-valorem term ($\widehat{\tau}^{adv}$, in \%} }   \\ \hline
Mean  & 5.4 & 3.4 & 2.8 & 2.8 & 2.4 & 2.1  \\
Median & 4.9 & 3.0 & 2.4 & 2.5 & 2.6 & 1.8 \\
%Standard Error & 0.043 & 0.026 & \multicolumn{1}{c}{0.025} & \multicolumn{1}{c}{0.021} & \multicolumn{1}{c}{0.016} & \multicolumn{1}{c}{0.013}  \\
\hline
\multicolumn{7}{l}{\textit{Additive term ($\widehat{t}^{add}/\widetilde{p}$, in \%} }   \\ \hline
Mean  & 4.6 & 2.6 & 3.1 & 2.4 & 2.1 & 1.5  \\
Median & 2.9 & 1.3 & 1.9 & 1.5 & 1.3 & 0.8 \\
%Standard Error & 0.068 & 0.044 & \multicolumn{1}{c}{0.037} & \multicolumn{1}{c}{0.035} & \multicolumn{1}{c}{0.031} & \multicolumn{1}{c}{0.023} \\ 
\hline
\# observations & 19196 & 17916 & \multicolumn{1}{c}{29387} & \multicolumn{1}{c}{36677} & \multicolumn{1}{c}{37643} & \multicolumn{1}{c}{38820} \\
\hline\hline
\multicolumn{7}{l}{\parbox[l]{11cm}{ \vspace{7pt}\scriptsize{Notes: TC = Transport Costs. Statistics are obtained weighting each observation by its value in transport (mode-dependent). Additive term expressed in fraction of fas price.}}}
\end{tabular}%
\end{center}
\label{tab:result_ves_rob}%
\end{table}%

@@

We now report the goodness-of-fit exercise (conducted by transport mode) at the 4-digit product classification level (for the selected years). The results are reported in Tables \ref{tab:good_fit_air_rob} (for Air) and \ref{tab:good_fit_ves_rob} (for Vessel).
\begin{table}[htbp]
  \centering
  \caption{Air: Measures of Goodness-of-fit, 4-digits}
\begin{center}
\label{tab:good_fit_air_rob}%
%\vspace{0.5cm}
%\scalebox{0.97}{
\begin{tabular}{l|cccccc}
\hline
\hline
      & \multicolumn{6}{c}{Year}              \\
      & \multicolumn{1}{c}{1974} & \multicolumn{1}{c}{1981} & \multicolumn{1}{c}{1989} & \multicolumn{1}{c}{2001} & \multicolumn{1}{c}{2009} & \multicolumn{1}{c}{2013}  \\
\hline
\textbf{R2} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &       &       &      \\
Model (A)& \multicolumn{1}{c}{0.48} & \multicolumn{1}{c}{0.49} & \multicolumn{1}{c}{0.50} & \multicolumn{1}{c}{0.50} & \multicolumn{1}{c}{0.45} & \multicolumn{1}{c}{0.35} \\
Model (B) & \multicolumn{1}{c}{0.63} & \multicolumn{1}{c}{0.66} & \multicolumn{1}{c}{0.65} & \multicolumn{1}{c}{0.66} & \multicolumn{1}{c}{0.54} & \multicolumn{1}{c}{0.45} \\
\textbf{SER} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &       & \multicolumn{1}{c}{} & \multicolumn{1}{c}{}  \\
Model (A)& \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &       & \multicolumn{1}{c}{0.88} & \multicolumn{1}{c}{0.93}  \\
Model (B) & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &       & \multicolumn{1}{c}{0.80} & \multicolumn{1}{c}{0.86}  \\
\textbf{Log-likelihood} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &       & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} \\
Model (A) & \multicolumn{1}{c}{-17505.55} & \multicolumn{1}{c}{-21813.46} & \multicolumn{1}{c}{-30960.56} & \multicolumn{1}{c}{-44067.62} & \multicolumn{1}{c}{-49375.57} & \multicolumn{1}{c}{-53197.87}  \\
Model (B) & \multicolumn{1}{c}{-14895.81} & \multicolumn{1}{c}{-18589.91} & \multicolumn{1}{c}{-26553.53} & \multicolumn{1}{c}{-37297.93} & \multicolumn{1}{c}{-45747.57} & \multicolumn{1}{c}{-49899.14}  \\
\textbf{AIC criteria} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} & \multicolumn{1}{c}{} &       & \multicolumn{1}{c}{}  \\
Model (A)& \multicolumn{1}{c}{36243.10} & \multicolumn{1}{c}{44966.91} & \multicolumn{1}{c}{63417.12} & \multicolumn{1}{c}{89747.24} & \multicolumn{1}{c}{100317.13} & \multicolumn{1}{c}{107963.73} \\
Model (B) & \multicolumn{1}{c}{31873.63} & \multicolumn{1}{c}{39495.82} & \multicolumn{1}{c}{55777.05} & \multicolumn{1}{c}{77439.85} & \multicolumn{1}{c}{94059.14} & \multicolumn{1}{c}{102224.28}  \\
\textbf{Test LL} &       &       &       &       &       &       \\
2$\times$(ll(UR) -ll(R)) & \multicolumn{1}{c}{5219.47} & \multicolumn{1}{c}{6447.09} & \multicolumn{1}{c}{8814.06} & \multicolumn{1}{c}{13539.39} & \multicolumn{1}{c}{7255.99} & \multicolumn{1}{c}{6597.45}  \\
\# restrictions  & \multicolumn{1}{c}{640} & \multicolumn{1}{c}{698} & \multicolumn{1}{c}{778} & \multicolumn{1}{c}{833} & \multicolumn{1}{c}{824} & \multicolumn{1}{c}{818}  \\
p-value & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.000} & \multicolumn{1}{c}{0.000} \\
\hline\hline
\multicolumn{7}{l}{\parbox[l]{15cm}{ \vspace{7pt}\scriptsize{Notes: Model (A) = with only ad-valorem transport costs. Model (B) = with additive \& ad-valorem
transport costs. R$^{2}$ between the log of predicted ratio and the log of the observed ratio. The number \# of restrictions is equal to the number of parameters estimated, i.e., the number of partner countries plus the number of products.}}}
\end{tabular}%
\end{center}
\end{table}%
